### 2023-02-22 text/ManuscriptDraft.Rmd
Editions to manuscript

---
new_session: FALSE
#title: |
#  **Detecting small objects and many of them: Using computer vision and deep learning to automate counting of collembola in petri dish samples**
#date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 12pt
geometry: margin = 1in
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{dcolumn}
- \usepackage{caption}
- \usepackage{float}
- \usepackage{afterpage}
- \usepackage{siunitx}
- \usepackage{amsmath}
#keywords: X
bibliography: ./library.bib
csl: ./journal-of-ecology.csl
---

@@

-	Overview of method
o	Standard method
o	Translating binary to bounding box format for model training
o	Splitting image/annotation data into training, validation, and testing sets
o	Slicing images/annotations for full resolution training
o	Training and testing neural network with sliding window approach

@@

Set         Images    Objects
Training    
Validation    
Testing

TO DO	# images	# objects
Train	89	
Val	19	
Test	19	
Total	127

## Training and testing neural network with sliding window approach
Just do the slice+SAHI approach and compare with standard 640x640.

@@

@@

@@

-	What did we present
-	Who can use it – and how
o	Model ready to test
o	Code available for training on new data and adaption
-	High resolution images taken in a standardized setting for training and production likely to improve results and should be considered in future studies.
-

>>>>

---
new_session: FALSE
#title: |
#  **Detecting small objects and many of them: Using computer vision and deep learning to automate counting of collembola in petri dish samples**
#date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 12pt
geometry: margin = 1in
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{dcolumn}
- \usepackage{caption}
- \usepackage{float}
- \usepackage{afterpage}
- \usepackage{siunitx}
- \usepackage{amsmath}
#keywords: X
bibliography: ./library.bib
csl: ./journal-of-ecology.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

-   Overview of method
-   Standard method
-   Translating binary to bounding box format for model training
-   Splitting image/annotation data into training, validation, and
    testing sets
-   Slicing images/annotations for full resolution training
-   Training and testing neural network with sliding window approach

@@

Set Images Objects Training\
Validation\
Testing

TO DO \# images \# objects Train 89\
Val 19\
Test 19\
Total 127

## Training and testing neural network with sliding window approach

Just do the slice+SAHI approach and compare with standard 640x640.

@@

## Resolution per petri dish

To investigate the influence of image resolution on detection
performance, we measured the number of pixels within the limits of the
petri dish in each image.

@@

### Standard approach

### Slicing

@@

-   What did we present
-   Who can use it -- and how o Model ready to test o Code available for
    training on new data and adaption
-   High resolution images taken in a standardized setting for training
    and production likely to improve results and should be considered in
    future studies.
-
